\begin{thebibliography}{9}
  \bibitem{Altarelli}
  Altarelli F, Monasson R, Semerjian G, Zamponi F.
  \textit{A review of the Statistical Mechanics approach to Random Optimization Problems.} Handbook of Satisfiability (2009)

  \bibitem{Henelius}
  Henelius P, Girvin S.
  \textit{A statistical mechanics approach to the factorization problem.} arXiv:1102.1296

  \bibitem{Chamon}
  Chamon C, Mucciolo E R, Ruckenstein A E, Yang Z-C. \textit{Quantum vertex model for reversible classical computing.} Nature Communications 8 (2017)

  \bibitem{Cerny}
  Černý V. \textit{Thermodynamical approach to the traveling salesman problem: An efficient simulation algorithm.} Journal of Optimization Theory and Applications, Volume 45, Issue 1, pp 41–51 (1985)

  \bibitem{Kirkpatrick2}
  Kirkpatrick S, Gelatt C D Jr., Vecchi M P. \textit{Optimization by Simulated Annealing}. Science VOL 220 (1983)

  \bibitem{SA}
  van Laarhoven P J, Aarts E. \textit{Simulated Annealing: Theory and Applications.} Springer (1987)

  \bibitem{Metropolis}
  Metropolis N, Rosenbluth A W, Rosenbluth  M N, Teller A H, Teller E. \textit{Equation of State Calculations by Fast Computing Machines.} J. Chem. Phys. 21 (1953) 1087-1092

  \bibitem{Sethna}
  Sethna J P.
  \textit{Entropy, Order Parameters, and Complexity}. Oxford University Press (2006)

  \bibitem{M-H_algorithm}
  Chib S, Greenberg E. \textit{Understanding the Metropolis-Hastings Algorithm}.The American Statistician, Vol. 49, No. 4. (1995)

  \bibitem{Garey}
  Garey M R, Johnson D S. \textit{Computers and Intractability: A Guide to the Theory of NP-Completeness}. W. H. Freeman and Company (1979)

  \bibitem{Cook}
  Cook S. \textit{The Complexity of Theorem-Proving Procedures.} Proceedings of the 3rd Annual ACM Symposium on Theory of Computing (1971)

  \bibitem{Monasson}
  Monasson R, Zecchina R, Kirkpatrik S, Selman B, Troyansky L.
  \textit{Determining computational complexity from characteristic `phase transitions'}. Nature VOL 400 (1999)

  \bibitem{Kirkpatrick}
  Kirkpatrick S, Selman B. \textit{Critical Behavior in the Satisfiability of Random Boolean Expressions.} Science VOL 264 (1994)

  \bibitem{Barahona}
  Barahona, F. \textit{On the computational complexity of Ising spin glass models.} J. Phys. A: Math. Gen. 15 (1982)

  \bibitem{Chamon_entropies}
  Chamon C, Mucciolo E R. \textit{Rényi entropies as a measure of the complexity of counting problems}. J. of Statistical Mechanics: Theory and Experiment (2013)

  \bibitem{Mauro}
  Mauro J C, Smedskjaer M M. \textit{Statistical mechanics of glass}. Journal of Non-Crystalline Solids (2014)

  \bibitem{Carleo}
  Carleo G, Becca F, Schirò M, Fabrizio M.
  \textit{Localization and Glassy Dynamics Of
Many-Body Quantum Systems.} Scientific Reports 2, Article number: 243 (2012)

  \bibitem{Mackenzie}
  Mackenzie N D, Young A P. \textit{Lack of Ergodicity in the Infinite-Range Ising Spin-Glass}. Physical Review Letters (1982)

  \bibitem{Complex_behavior_of_glassy_systems}
  Rubí M, Pérez-Vincente C. \textit{Complex Behaviour
of Glassy Systems}. Springer (1997)

  \bibitem{Istrail}
  Istrail S.
  \textit{Statistical mechanics, three-dimensionality and NP-completeness. I. Universality of intractability for the partition function of the Ising model across non-planar lattices}. Proceedings of the Thirty-Second Annual ACM Symposium on Theory of Computing (2000)

  \bibitem{Lucas}
  Lucas A. \textit{Ising formulations of many NP problems}.Front. Phys. (2014)

  \bibitem{Toffoli}
  Toffoli T. \textit{Reversible Computing.} Proceedings of the 7th Colloquium on Automata, Languages and Programming (1980)

  \bibitem{Biamonte}
  Biamonte J D.
  \textit{Nonperturbative k-body to two-body commuting conversion Hamiltonians and embedding problem instances into Ising spins}. Phys. Rev. A VOL 77, 052331 (2008)

\end{thebibliography}
